\large Neural and Symbolic Optimization of Cosmological Particle-Mesh Simulation \vspace{0.3em}

### 2024-02-06 docs/papers/sto/so.tex
FIXUP draft updates

% hardware setups
We perform distributed data-parallel training using GPU devices hosted on
multiple CPU nodes.
With each process being binded to a single GPU device, the training data samples
are uniformly distributed to the processes.
In total, we use [...] \GPU\ GPUs, each accompanied with [...] CPU cores and
[...] GB CPU memory mainly for preloading the training data.
In each training step, a data sample is fed into the GPU from the CPU memory
where the preloading takes place to save the reading time from the disk.

Following \autoref{tab:param}, in each iteration, we randomly sample the number
of time steps and the mesh shape, and configure \pmwd\ with the same initial
coniditions, cosmological parameters and other common configurations.
To balance the work of GPUs during training, in each iteration we use
the same number of time steps and mesh shape on all GPUs.

As discussed in \autoref{sec:loss}, the loss in a single simulation sums over
all snapshots.
Our batch size is [...], i.e. the number of GPU devices since one simulation is
run on a given GPU and compared to the corresponding training data sample for
loss.
For each training step, the loss and gradients are collected and averaged across
all GPU devices.
The SO parameters are initialized to be the same for all devices, and being
updated with the same averaged gradients.

The SO MLP parameters are initialized in a way such that the MLP output is very
close to one, i.e. no SO.
We achieve this by setting the kernel of the output layer to be very small
random values and the bias to be one.

@@

\vspace{1em}
\subsection{Symbolic Regression Fitting of the Neural Networks}

>>>>

We perform distributed data-parallel training using GPU devices hosted
on multiple CPU nodes.
With each process being binded to a single GPU device, the training data
samples are uniformly distributed to the processes.
In total, we use [...] \GPU\ GPUs, each accompanied with [...] CPU cores
and [...] GB CPU memory mainly for preloading the training data.
In each training step, a data sample is fed into the GPU from the CPU
memory where the preloading takes place to save the reading time from
the disk.

For each training step, we configure and run \pmwd\ with the same
initial coniditions, cosmological parameters and other common
configurations as the training data sample.
As discussed in \autoref{sec:loss}, the loss in a single simulation sums
over all snapshots.
Our batch size is [...], i.e. the number of GPU devices, since one
simulation is run on a single GPU and compared to the corresponding
training data sample for loss.
Then the loss and gradients are collected and averaged across all GPU
devices, with which the optimizer is also updated.
The SO parameters are initialized to be the same for all devices, and
hence remain the same for all processes given the same averaged
gradients.
We use the Adam \citep{Adam} optimizer.

The SO NN parameters are initialized in a way such that the output
is very close to one, i.e. no SO.
We achieve this by setting the kernel of the output layer to be very
small random values and the bias to be zero, which is around one after
the exponential function.

@@

\vspace{1em}
\subsection{Symbolic Regression Fitting}
